On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-03-26 engineering.tex
add paragraph name "port weaknesses"
port proof (first draft)

While \emph{agents} and \emph{communication} between agents are described and
defined in Section~\ref{sec:theory}, both the concepts of \emph{port},
\emph{channel}, \emph{functional and physical architecture}, and
\emph{functional block} have not yet been defined with respect to the
$\abf$-theory.  Informally, a channel identifies the place where the
communication takes place.  In this work we only consider mono-directional
channels and communication but the extension to bi-directional channel can be
considered as the union of two unidirectional channels. A mono-directional
channel is defined by the assertions sent or received (over the channel).

@@

\begin{definition}{\bf Secure Input Port --}\label{def:secport}
	A secure input port allows information as incoming assertions to flow
	from a sender $s$ to the behavior of the recipient $a$ (agent).  If $p_I$ is a secure input port,
	$\world\models\varphi$, and $\varphi\in\assertionRegion_s$ where $s$
	has the only input port $p_I$, $\world'\models\beliefRegion_a$ and $\varphi\in\beliefRegion_a$.
\end{definition}
From this definition, it follows that there exist only the following types of insecure port in RCC5:
\begin{itemize}
	\item \emph{drop port} ($s\circ\rightarrow a$), where assertions reaches the port but do not pass the boundary of the agent (i.e. do not become belief of the agent)
	\item \emph{insertion port} ($s\rightarrow\bullet a$), where some new information is believed by $a$ as incoming from the port but $s$ didn't send it
	\item \emph{injection port} ($s\circ\rightarrow\bullet a$), where information coming from $s$ is substituted with new information which becomes believed by $a$
	\item \emph{selective port} ($s\hookrightarrow a$), where some
		information passes the port while other is either dropped
		($s\circ\hookrightarrow a$), inserted
		($s\hookrightarrow\bullet a$), or injected
		($s\circ\hookrightarrow\bullet a$)
\end{itemize}

\begin{proof}

\end{proof}

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=.9\textwidth]{IOports.pdf}
	\caption{Input and Output Port of an agent}
	\label{fig:ioports}
\end{figure}

While \emph{agents} and \emph{communication} between agents are described and
defined in Section~\ref{sec:theory}, both the concepts of \emph{port} (depicted in Figure~\ref{fig:ioports},
\emph{channel}, \emph{functional and physical architecture}, and
\emph{functional block} have not yet been defined with respect to the
$\abf$-theory.  Informally, a channel identifies the place where the
communication takes place.  In this work we only consider mono-directional
channels and communication but the extension to bi-directional channel can be
considered as the union of two unidirectional channels. A mono-directional
channel is defined by the assertions sent or received (over the channel).

@@

\begin{definition}{\bf Secure Input Port --}\label{def:secport}
	A secure input port allows information as incoming assertions to flow
	from a sender $s$ to the behavior of the recipient $a$ (agent).  If $p_I$ is a secure input port,
	$\world\models\varphi$, and $\varphi\in\assertionRegion_s$ where $s$
	has the only input port $p_I$, $\world'\models\beliefRegion_a$ and $\varphi\in\beliefRegion_a$.
\end{definition}

\Paragraph{Port weaknesses}
From this definition, it follows that there exist only the following types of insecure port in RCC5:
\begin{itemize}
	\item \emph{drop port} ($s\dropport a$), where assertions reaches the port but do not pass the boundary of the agent (i.e. do not become belief of the agent)
	\item \emph{insertion port} ($s\insertport a$), where some new information is believed by $a$ as incoming from the port but $s$ didn't send it
	\item \emph{injection port} ($s\injectionport a$), where information coming from $s$ is substituted with new information which becomes believed by $a$
	\item \emph{selective port}, where some
		information passes the port while other is either dropped
		($s\selectivedropport a$), inserted
		($s\selectiveinsertport a$), or injected
		($s\selectiveinjectionport a$)
\end{itemize}

\begin{proof}
An input port is, in the $\abf$-theory, defined secure as long as the relation
	between the two regions of input assertions $\assertionRegion$ and
	output beliefs $\beliefRegion$ are equal, i.e.
	$\eq{\assertionRegion}{\beliefRegion}$. Therefore, any other relation
	should result in a weakness (related to an insecurity flaw) of that
	input port.  Using RCC5, there exist exactly other $4$ different type
	of relations, one of which is the discrete-from (DR) relation, i.e.
	$\dr{\assertionRegion}{\beliefRegion}$. When two regions are related by
	the DR relations, they have no element (subregion) in common. Lets
	define a function weight $|X|$ such as, for any region $X$, it
	represents the smallest possible cardinality of a topological base for
	$X$; where a base is a collection of regions in a topology such that
	every open region can be written as union of elements of that base.  If
	$\dr{\assertionRegion}{\beliefRegion}$ there exist only two mutually
	exclusive options: either $|\assertionRegion|=|\beliefRegion|$ or
	$|\assertionRegion|\neq|\beliefRegion|$. If, at the end of a
	communication through the input-port
	$|\assertionRegion|\neq|\beliefRegion|$, the two regions have a
	different number of subregions and then there exist only two mutually
	exclusive options: 
	\begin{itemize}
		\item either $|\assertionRegion|>|\beliefRegion|$, where one
			ore more assertions didn't become Beliefs, which we
			call \emph{drop port} since its behavior drops and
			prevents incoming communications,
		\item or $|\assertionRegion|<|\beliefRegion|$, where there are
			one ore more Beliefs which have not been sent as
			incoming communication, which we call \emph{insertion
			port} since its behavior generates new Beliefs
			unrelated to the incoming communications. 
	\end{itemize}
	If $|\assertionRegion|=|\beliefRegion|$, given that information is monotone by nature (due to its entropy)
there exist only two mutually
	exclusive options: 
	\begin{itemize}
		\item either information has been generated and transferred, increasing the cardinality of both
			$\assertionRegion$ and $\beliefRegion$, i.e.
			$|\assertionRegion_{t^0}|>|\assertionRegion_{t^1}|$ and
			$|\beliefRegion_{t^0}|>|\beliefRegion_{t^1}|$ (where
			$t^0$ and $t^1$ represent time at the beginning of
			communication and right after respectively), which
			means that Assertions has reached the port and new
			Belief have been generated by the port but no
			correlation the elements of the two regions exist, and
			we call it \emph{injection port} since it has modified
			the information carried by the assertions into new
			corresponding beliefs.
		\item or $|\assertionRegion_{t^0}|=|\assertionRegion_{t^1}|$
			and $|\beliefRegion_{t^0}|=|\beliefRegion_{t^1}|$ but
			this implies that no communication occurred, while we
			assumed that a communication was taking place (absurd).
	\end{itemize}
	Similarly, 
	\begin{itemize}
		\item given that $\dr{\assertionRegion}{\beliefRegion}$ is
			$\dr{\assertionRegion}{\beliefRegion}$ except for the
			intersection in which case is
			$\eq{\assertionRegion}{\beliefRegion}$ (see
			\autocite{Santaca2016abf}),
			we call it a selective injection port ($s\selectivedropport a$),
		\item if $\pp{\assertionRegion}{\beliefRegion}$, we have that
			some Belief are not correlated to incoming assertion
			and we call it ($s\selectiveinsertport a$)
		\item if $\ppi{\assertionRegion}{\beliefRegion}$ we have that
			some incoming Assertions are not correlated to Belief 
			and we call it ($s\selectiveinjectionport a$)
	\end{itemize}
\end{proof}
